\documentclass[a4paper,10pt,sans]{moderncv}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}

\input{contactInformation}
\input{modernCVTheme}

\begin{document}

\maketitle

\section{Summary}
\begin{cvcolumns}
  \cvcolumn{}{%
    I am a software developer passionate in technologies since I was young.
    Since 2014, I have been working on Android Wear platform development for wearables and delivered the award-winning Tag Heuer Connected watches.
  }
\end{cvcolumns}

\section{Technical skills}
\begin{cvcolumns}
  \cvcolumn{Android}{%
    \begin{itemize}
      \item Platform development
      \item Hardware bring-up
      \item New product enabling
      \item Product development
      \item System debugging
      \item Knowledge from linux kernel to apps (java)
    \end{itemize}
  }
  \cvcolumn{Languages}{%
    \begin{itemize}
    \item C
    \item C++
    \item Git
    \item Python
    \item Java
    \item Bash
    \end{itemize}
  }
  \cvcolumn{Other}{%
    \begin{itemize}
      \item Linux kernel \& userspace
      \item Embedded systems
      \item Operating systems
      \item Software development
      \item Manufacturing support
      \item Spacemacs
    \end{itemize}
  }
\end{cvcolumns}
    
\section{Key accomplishments}
\begin{cvcolumns}
  \cvcolumn{Audio software stack}{%
    I was the audio software stack owner on Android Wear based products.
    I have developed and debugged several places in the software stack including DSP firmware, Linux kernel drivers, Audio HALs and apps (java).
  }
\end{cvcolumns}
\begin{cvcolumns}
  \cvcolumn{Custom Android ROM for production line}{%
    Traveled two weeks to China for pre-mass production, on-site troubleshooting and support.
    Designed and implemented Intel wearable Manufacturing OS (based on Android), for hardware testing on the production line.
  }
\end{cvcolumns}
\begin{cvcolumns}
  \cvcolumn{Platform bring-up}{%
    Traveled one week to the Bay Area for a hard-ware bring-up. Audio stack (with codec, speakers, four microphones) was up in two days and had three more days to make the camera work.
  }
\end{cvcolumns}
\begin{cvcolumns}
  \cvcolumn{Multiple products}{%
    I worked on several Intel based Android Wear products such as Fossil Q Founder, Tag Heuer Connected 46, Tag Heuer Connected Modular 45 and New Balance RunIQ.
  }
\end{cvcolumns}


\section{Work history}
\subsection{Intel New Device Group}
\cventry{Feb, 2017 -- Current}{Android platorm engineer}{CELAD}
{San Francisco Bay Area}{}
{%
  \begin{itemize}
  \item Android platform engineer on Android Wear products with Intel inside
  \item Active during entire product lifecycle from the early schematics to the end-user software releases.
  \item Several roles including platform developer, system debugger, and factory line support.
  \item Technical skills:
    \begin{itemize}
    \item Android/Linux device drivers (ASoC), intel platform drivers
    \item Android frameworks: audio HALs, other HALs, Treble
    \item Android apps: mainly debugging, no development.
    \item Production line support, system debugging, hardware bring-ups
    \item Linux, C, C++, Java, Git, Python, XML, Bash, Android build system
    \end{itemize}
  \end{itemize}
}

\cventry{Sept, 2014 -- Jan, 2017}{Android platform engineer}{CELAD}
{}{France}
{
    \begin{itemize}
    \item Android platform engineer on Android Wear products with Intel inside
    \item Implemented Android Audio stack (HAL, linux machine driver (ASoC)) for digital microphone (voice recognition)
    \item Developed a low-power bluetooth audio playback architecture (A2DP)
    \item Designed a custom Android ROM used for mass production testing and quality screening in the factory.
    \item Technical skills:
      \begin{itemize}
        \item Android/Linux device drivers (ASoC framework) and DSP Firmware
        \item Android frameworks: audio HAL, AudioFlinger, AudioPolicy
        \item Production line support, system debugging, hardware bring-ups
        \item Linux, C, C++, Git, Python, XML, Bash, Android build system
      \end{itemize}
    \end{itemize}
}

\subsection{Internships}
\cventry{Apr, 2014 -- Aug, 2014}{Android Audio developer}{CELAD}
{}{France}
{
  \begin{itemize}
    \item Open-sourced the Parameter-Framework, a major component of Intel's Android Audio HAL
    \item Component is now part of Android AOSP (/external/parameter-framework/)
    \item Extended audio stack on Intel phone reference platforms (dual sim)
    \item Technical skills:
    \begin{itemize}
      \item Linux, C, C++ Git, XML, markdown, Android platform
    \end{itemize}
  \end{itemize}
}

\cventry{May, 2013 -- Aug, 2013}{Windows embedded developer}{24green}
{}{The Netherlands}
{
  \begin{itemize}
    \item Developed a web (REST) API which handles climate control functions in green-houses.
    \item Created apps to illustrate the API.
    \item Technical skills:
    \begin{itemize}
      \item C\#, Windows XP embedded
      \item javascript, html, CSS, java
    \end{itemize}
  \end{itemize}
}

\cventry{Apr, 2012 -- Jul, 2012}{Linux kernel developer}{IRIT}
{}{France}
{
  \begin{itemize}
    \item Linux kernel development around performance counters and other hardware metrics
    \item Modules developed used by research lab for experiments on CPU frequency (power savings)
    \item Real world testing on a French research grid computing network, Grid'5000
    \item Technical skills:
      \begin{itemize}
        \item Linux kernel, device drivers, C, GNU make, Bash
      \end{itemize}
  \end{itemize}
}


\section{Education}
\cventry{2009 -- 2014}{Paul Sabatier University}{Toulouse, France}{CAMSI (Informatics, Systems and Machine Architecture Concepts)}{Master's degree}
{
  \begin{itemize}
  \item rank 1/18 (Valedictorian)
  \item overall score > 85\%
  \end{itemize}
}


\end{document}
